---
title: "DataFest_Analysis"
output: pdf_document
author: "S^2LZ^2"
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, warning = F, message = F}
library(tidyverse)
library(knitr)
library(broom)
library(nnet) # for multinomial logistic regression
library(patchwork)
```


## R Markdown

```{r load-datasets, warning=FALSE, message=FALSE}
CA <- read_csv("~/df_data/CA/ca.csv")
DE <- read_csv("~/df_data/DE/de.csv")
UK <- read_csv("~/df_data/UK/uk.csv")
US18 <- read_csv("~/df_data/US/us_18.csv")
US19 <- read_csv("~/df_data/US/us_19.csv")

```

## Including Plots

```{r , echo=FALSE, warning=FALSE, message=FALSE}
#Check the sums of na in each column for all Data Sets. 
tidy(colSums(is.na(UK)))
tidy(colSums(is.na(CA)))
tidy(colSums(is.na(US18)))
tidy(colSums(is.na(US19)/nrow(US19)))
tidy(colSums(is.na(US19)))
tidy(colSums(is.na(DE)))
  
  
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



```{r AreYouInCollege-drug-misuse-visual, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(DEM_COLLEGE), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No",
                              "1" = "Yes",
                            "NA" = "Not a Student in the past 3 months"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Student", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")

ggplot(data = US18, aes(x = factor(DEM_COLLEGE), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No",
                              "1" = "Yes",
                            "NA" = "Not a Student in the past 3 months"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Student", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")

ggplot(data = US18, aes(x = factor(DEM_COLLEGE), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No",
                              "1" = "Yes",
                            "NA" = "Not a Student in the past 3 months"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Student", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")



```

```{r SchoolTypes-drug-misuse-visual, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")

ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")

ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")


```

```{r collegeLength-Drug-Misuse-visual, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")

ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")

ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")

```

```{r collegeSize-drug-misuse-visual, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_SIZE), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "< 5,000", "1" = "5,000 - 10,000",
                              "2" = "10,001 - 25,000",
                            "3" = "> 25,000", 
                            "4" = "Not Sure", 
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Your School Size", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")

ggplot(data = US18, aes(x = factor(COLLEGE_SIZE), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "< 5,000", "1" = "5,000 - 10,000",
                              "2" = "10,001 - 25,000",
                            "3" = "> 25,000", 
                            "4" = "Not Sure", 
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Your School Sizey", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")

ggplot(data = US18, aes(x = factor(COLLEGE_SIZE), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "< 5,000", "1" = "5,000 - 10,000",
                              "2" = "10,001 - 25,000",
                            "3" = "> 25,000", 
                            "4" = "Not Sure", 
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Your School Size", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")

```

```{r collegeHousing-Drug-Misuse-visual, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_HOUSING), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Do you currently live in on-campus housing", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")

ggplot(data = US18, aes(x = factor(COLLEGE_HOUSING), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Do you currently live in on-campus housing", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")

ggplot(data = US18, aes(x = factor(COLLEGE_HOUSING), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Do you currently live in on-campus housing", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")

```

```{r visual, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among Greeklife Students")

ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among Greeklife Students")

ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among Greeklife Students")

```

factor(FENT_NMU,
    BUP_NMU,
    METH_NMU,
    MORPH_NMU,
    OXY_NMU,
    OXYM_NMU,
    TRAM_NMU,
    TAP_NMU, 
    HYD_NMU, 
    HYDM_NMU,
    SUF_NMU, 
    COD_NMU, 
    DIHY_NMU 
    )

### Which of Pain Relief Med Has Been Misused the Most?


```{r}
US18%>%
  count("FENT_NMU")

US18%>%
  count("BUP_NMU")

US18%>%
  count("METH_NMU")

US18%>%
  count("MORPH_NMU")

US18%>%
  count("OXY_NMU")

US18%>%
  count("OXYM_NMU")

US18%>%
  count(
    "TRAM_NMU")

US18%>%
  count(
    "TAP_NMU")

US18%>%
  count(
    "HYD_NMU")

US18%>%
  count(
    "HYDM_NMU")

US18%>%
  count(
    "SUF_NMU")

US18%>%
  count( 
    "COD_NMU")

US18%>%
  count(
    "DIHY_NMU")

```
The medication that has the greatest number of 1s is Hydrocodone (HYD_NMU.)
```{r}
ggplot(data = US18, aes(x = factor(DEM_COLLEGE), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No",
                              "1" = "Yes",
                            "NA" = "Not a Student in the past 3 months"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Student", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")

ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among Greeklife Students")
###############################

ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
#############################################

ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
####################################

ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
#############################################

ggplot(data = US18, aes(x = factor(COLLEGE_SIZE), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "< 5,000", "1" = "5,000 - 10,000",
                              "2" = "10,001 - 25,000",
                            "3" = "> 25,000", 
                            "4" = "Not Sure", 
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Your School Size", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
#############################################

ggplot(data = US18, aes(x = factor(COLLEGE_HOUSING), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Do you currently live in on-campus housing", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
#############################################

ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among Greeklife Students")

```

Among all three drug classes plus Hydrocodone, trade school unvariably have the
highest proportion of people who reported that they had used a prescription 
medication without Doctor's prescription.

### Why?
```{r}
#I didn't leave every graph in, but Trade school has pretty much the highest proportion for 68-71
ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(HPC_SELL)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
```


###Which group of people has the highest likelihood to have drug misuses?


###Which group of people are more likely to seek for help for drug misuses?



