---
title: "DataFest_Analysis"
output: pdf_document
author: "S^2LZ^2"
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, warning = F, message = F}
library(tidyverse)
library(knitr)
library(broom)
library(nnet) # for multinomial logistic regression
library(patchwork)
```


## R Markdown

```{r load-datasets, warning=FALSE, message=FALSE}
# CA <- read_csv("~/df_data/CA/ca.csv")
# DE <- read_csv("~/df_data/DE/de.csv")
# UK <- read_csv("~/df_data/UK/uk.csv")
US18 <- read.csv("~/df_data/US/us_18.csv", na.strings=c(""))
# US19 <- read_csv("~/df_data/US/us_19.csv")

```

## Including Plots

```{r , echo=FALSE, warning=FALSE, message=FALSE}
#Check the sums of na in each column for all Data Sets. 
tidy(colSums(is.na(UK)))
tidy(colSums(is.na(CA)))
tidy(colSums(is.na(US18)))
tidy(colSums(is.na(US19)/nrow(US19)))
tidy(colSums(is.na(US19)))
tidy(colSums(is.na(DE)))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


```{r AreYouInCollege-drug-misuse-visual-BENZ, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(DEM_COLLEGE), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No",
                            "1" = "Yes",
                            "NA" = "Not a Student in the past 3 months"))+
  theme_classic() +
  labs(y = "Proportion", 
       x = "Are You A Student", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")
```


```{r AreYouInCollege-drug-misuse-visual-THC, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(DEM_COLLEGE), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                "Never Used")) +
  scale_x_discrete(labels=c("0" = "No",
                              "1" = "Yes",
                            "NA" = "Not a Student in the past 3 months"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Student", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")
```


```{r AreYouInCollege-drug-misuse-visual-STIM, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(DEM_COLLEGE), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No",
                              "1" = "Yes",
                            "NA" = "Not a Student in the past 3 months"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Student", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")



```

```{r SchoolTypes-drug-misuse-visual-BENZ, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")
```


```{r SchoolTypes-drug-misuse-visual-THC, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")
```
Students who identify as enrolled in "other" type of schools has a higher proportion
of using a THC without a doctor's prescription.

```{r SchoolTypes-drug-misuse-visual-STIM, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")


```

```{r collegeLength-Drug-Misuse-visual-BENZ, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "College length", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")
```
Trade school and other (?) has a higher proportion of students using Benzodiazepine
without a doctors' prescription.

```{r collegeLength-Drug-Misuse-visual-THC, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")
```


```{r collegeLength-Drug-Misuse-visual-STIM, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")

```
Trade school students as a higher proportion of students using a stimulant
without a doctors' prescription.

```{r collegeSize-drug-misuse-visual-BENZ, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_SIZE), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "< 5,000", "1" = "5,000 - 10,000",
                              "2" = "10,001 - 25,000",
                            "3" = "> 25,000", 
                            "4" = "Not Sure", 
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Your School Size", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")
```


```{r collegeSize-drug-misuse-visualTHC, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_SIZE), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "< 5,000", "1" = "5,000 - 10,000",
                              "2" = "10,001 - 25,000",
                            "3" = "> 25,000", 
                            "4" = "Not Sure", 
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Your School Sizey", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")
```
Students who enrolled in a school of size >25,000 has a higher proportion of using
a THC without a doctor's prescription.

```{r collegeSize-drug-misuse-visual-THC, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_SIZE), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "< 5,000", "1" = "5,000 - 10,000",
                              "2" = "10,001 - 25,000",
                            "3" = "> 25,000", 
                            "4" = "Not Sure", 
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Your School Size", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")

```
Students who enrolled in a school of size >25,000 has a higher proportion of using
a stimulant without a doctor's prescription.

```{r collegeHousing-Drug-Misuse-visual-BENZ, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_HOUSING), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Do you currently live in on-campus housing", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among College Students")
```


```{r collegeHousing-Drug-Misuse-visual-THC, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_HOUSING), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Do you currently live in on-campus housing", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among College Students")
```


```{r collegeHousing-Drug-Misuse-visual-STIM, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_HOUSING), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Do you currently live in on-campus housing", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among College Students")

```

```{r collegeGREEK-visual-BENZ, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(BENZ_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Benzodiazepine Without a Doctor’s Prescription ", 
       title = "Proportion of Benzodiazepine Misuse Among Greeklife Students")
```
Students in greeklife has a higher proportion of using benzo w/o doctor's 
prescription.

```{r collegeGREEK-visual-THC, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(THC_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a THC Without a Doctor’s Prescription ", 
       title = "Proportion of THC Misuse Among Greeklife Students")
```


```{r collegeGREEK-visual-STIM, warning=FALSE, message=FALSE}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(STIM_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Stimulant Without a Doctor’s Prescription ", 
       title = "Proportion of Stimulant Misuse Among Greeklife Students")

```

factor(FENT_NMU,
    BUP_NMU,
    METH_NMU,
    MORPH_NMU,
    OXY_NMU,
    OXYM_NMU,
    TRAM_NMU,
    TAP_NMU, 
    HYD_NMU, 
    HYDM_NMU,
    SUF_NMU, 
    COD_NMU, 
    DIHY_NMU 
    )

### Which of Pain Relief Med Has Been Misused the Most?


```{r}
US18%>%
  count("FENT_NMU")

US18%>%
  count("BUP_NMU")

US18%>%
  count("METH_NMU")

US18%>%
  count("MORPH_NMU")

US18%>%
  count("OXY_NMU")

US18%>%
  count("OXYM_NMU")

US18%>%
  count(
    "TRAM_NMU")

US18%>%
  count(
    "TAP_NMU")

US18%>%
  count(
    "HYD_NMU")

US18%>%
  count(
    "HYDM_NMU")

US18%>%
  count(
    "SUF_NMU")

US18%>%
  count( 
    "COD_NMU")

US18%>%
  count(
    "DIHY_NMU")

```
The medication that has the greatest number of 1s is Hydrocodone (HYD_NMU.)

```{r}
ggplot(data = US18, aes(x = factor(DEM_COLLEGE), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No",
                              "1" = "Yes",
                            "NA" = "Not a Student in the past 3 months"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Student", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
```


```{r}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among Greeklife Students")
###############################
```
A higher proportion of Greeklife member report to have used hydrocodone w/o a 
doctor's prescription.

```{r}
ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
#############################################
```


```{r}
ggplot(data = US18, aes(x = factor(COLLEGE_TYPE), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "Public",
                              "1" = "Private",
                            "2" = "Other"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
####################################
```


```{r}
ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
#############################################
```

A higher proportion of trade school student report to have used hydrocodone w/o a 
doctor's prescription.

```{r}
ggplot(data = US18, aes(x = factor(COLLEGE_SIZE), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "< 5,000", "1" = "5,000 - 10,000",
                              "2" = "10,001 - 25,000",
                            "3" = "> 25,000", 
                            "4" = "Not Sure", 
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Your School Size", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
#############################################
```


```{r}
ggplot(data = US18, aes(x = factor(COLLEGE_HOUSING), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Do you currently live in on-campus housing", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among College Students")
#############################################
```


```{r}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(HYD_NMU)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among Greeklife Students")

```
Students in greeklife has a higher proportion of using hydrocodone w/o doctor's 
prescription.

Among all three drug classes plus Hydrocodone, trade school univariably have the
highest proportion of people who reported that they had used a prescription 
medication without Doctor's prescription.

### Why?
```{r}
# I didn't leave every graph in, but Trade school has pretty much the highest
# proportion for 68-71
ggplot(data = US18, aes(x = factor(COLLEGE_LENGTH), fill = factor(HPC_SELL)))+
  geom_bar(position = "fill")+
  coord_flip()+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "School Types", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of students who know of a healthcae professional colleague who took a controlled substance from the workpalce with the intent to sell")
```
A higher proportion of trade school students know of a healthcare professional 
colleague who took a controlled substance from the workplace with the intent to sell.

```{r regression model-THC}
students_US <- US18 %>% 
  filter(DEM_COLLEGE == 1)

model_initial_THC <- glm(THC_NMU ~ factor(COLLEGE_GREEK) + factor(HPC_SELL) + factor(COLLEGE_LENGTH) + factor(COLLEGE_TYPE) + factor(COLLEGE_SIZE),
                     data = students_US,
                     family = binomial)
tidy(model_initial_THC)
# backward_aic <- step(model_initial_THC) - error
```

```{r regression model-BENZ}
students_US <- US18 %>% 
  filter(DEM_COLLEGE == 1)

model_initial_BENZ <- glm(BENZ_NMU ~ factor(COLLEGE_GREEK) + factor(HPC_SELL) + factor(COLLEGE_LENGTH) + factor(COLLEGE_TYPE) + factor(COLLEGE_SIZE),
                     data = students_US,
                     family = binomial)
tidy(model_initial_BENZ)
backward_aic <- step(model_initial_BENZ)
```
HPC_SELL, \*COLLEGE_LENGTH (p-value big), COLLEGE_TYPE, COLLEGE_SIZE are significant 
predictors for benzo misuse.

```{r regression model-STIM}
students_US <- US18 %>% 
  filter(DEM_COLLEGE == 1)

model_initial_STIM <- glm(STIM_NMU ~ factor(COLLEGE_GREEK) + factor(HPC_SELL) + factor(COLLEGE_LENGTH) + factor(COLLEGE_TYPE) + factor(COLLEGE_SIZE),
                     data = students_US,
                     family = binomial)
tidy(model_initial_STIM)
# backward_aic <- step(model_initial_STIM) - error
```
```{r regression model-HYD}
students_US <- US18 %>% 
  filter(DEM_COLLEGE == 1)

model_initial_HYD <- glm(HYD_NMU ~ factor(COLLEGE_GREEK) + factor(HPC_SELL) + factor(COLLEGE_LENGTH) + factor(COLLEGE_TYPE) + factor(COLLEGE_SIZE),
                     data = students_US,
                     family = binomial)
tidy(model_initial_HYD)
backward_aic <- step(model_initial_HYD) 
```

COLLEGE_GREEK, \*HPC_SEL(p-value big), and \*COLLEGE_SIZE (p-value big) are significant predictors for hydrocodone misuse.

\textbf{Maybe look at interaction between COLLEGE_TYPE and HPC_SELL}

###Which group of people has the highest likelihood to have drug misuses?

### Question 3

##Which group of US college students are more likely to seek help for drug misuses?

```{r SeekHelp-Education Level}
ggplot(data = US18, aes(x = factor(DEM_EDU), fill = factor(HELP_SUB_USE)))+
  geom_bar(position = "fill") +
  coord_flip() + 
  scale_fill_discrete(labels = c("No", "Yes")) +
  scale_x_discrete(labels=c("1" = "Less than a year high school diploma",
                            "2" = "Regular high school/GED/Alt",
                            "3" = "Some college credit but no degree", 
                            "4" = "Trade school", 
                            "5" = "Associate degree", 
                            "6" = "Bachelors degree",
                            "7" = "Masters degree",
                            "8" = "Doctoral degree"))+
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(y = "Proportion", 
       x = "Education level", 
       title = "Proportion of people who have sought professional help for substance abuse by education level")
```

Students in trade school have a relatively higher proportion of seeking professional help for substance abuse.


```{r SeekHelp-Education Level}
ggplot(data = students_US, aes(x = factor(COLLEGE_TYPE), fill = factor(HELP_SUB_USE)))+
  geom_bar(position = "fill") +
  coord_flip() + 
  scale_fill_discrete(labels = c("No", "Yes")) +
scale_x_discrete(labels=c("0" = "Public",
                          "1" = "Private",
                          "2" = "Other")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(y = "Proportion", 
       x = "College type", 
       title = "Proportion of college students who have sought professional help for substance abuse by college type")
```
Students in private colleges have a higher proportion of seeking professional help for substance abuse.


```{r}
ggplot(data = students_US, aes(x = factor(COLLEGE_SIZE), fill = factor(HELP_SUB_USE)))+
  geom_bar(position = "fill") +
  coord_flip() + 
  scale_fill_discrete(labels = c("No", "Yes")) +
  scale_x_discrete(labels=c("0" = "< 5,000", "1" = "5,000 - 10,000",
                              "2" = "10,001 - 25,000",
                            "3" = "> 25,000", 
                            "4" = "Not Sure", 
                            "NA" = "Not A Student"))+
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(y = "Proportion", 
       x = "College size", 
       title = "Proportion of college students who have sought professional help for substance abuse by college size")
```
Students with a college size over 25,000 have a higher proportion of seeking professional help for substance abuse.

```{r}
ggplot(data = students_US, aes(x = factor(COLLEGE_LENGTH), fill = factor(HELP_SUB_USE)))+
  geom_bar(position = "fill") +
  coord_flip() + 
  scale_fill_discrete(labels = c("No", "Yes")) +
  scale_x_discrete(labels=c("1" = "2 Years College/Uni",
                              "2" = "4 Years College/Uni",
                            "3" = "Graduate School ", 
                            "4" = "Online School", 
                            "5" = "Trade School", 
                            "6" = "Other",
                            "NA" = "Not A Student")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(y = "Proportion", 
       x = "College length", 
       title = "Proportion of college students who have sought professional help for substance abuse by college length")
```

Students who are current in college school have a higher proportion of seeking professional help for substance abuse.


```{r}
ggplot(data = students_US, aes(x = factor(COLLEGE_GREEK), fill = factor(HELP_SUB_USE)))+
  geom_bar(position = "fill") +
  coord_flip() + 
  scale_fill_discrete(labels = c("No", "Yes")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(y = "Proportion", 
       x = "College length", 
       title = "Proportion of college students who have sought professional help for substance abuse by college length")

```
Students who are in Greek life have a higher proportion of seeking professional help for substance abuse.



### Question 2

##Why are US college students in fraternity/sorority more likely to have drug misuses?

```{r q68 greek}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(DRSHOP_USE)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among Greeklife Students")

```

```{r greek q69}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(DRSHOP_SELL)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among Greeklife Students")
```

```{r q69 greek}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(HPC_USE)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among Greeklife Students")
```
```{r}
ggplot(data = US18, aes(x = factor(COLLEGE_GREEK), fill = factor(HPC_SELL)))+
  geom_bar(position = "fill")+
  scale_fill_discrete(labels = c("No",  "Yes", 
                                  "Never Used")) +
  scale_x_discrete(labels=c("0" = "No", "1" = "Yes",
                              "NA" = "Not A Student"))+
  theme_classic() +
 labs(y = "Proportion", 
       x = "Are You A Member of A College Greeklife Organization", 
      fill = "Used a Hydrocodone Without a Doctor’s Prescription ", 
       title = "Proportion of Hydrocodone Misuse Among Greeklife Students")
```


```{r why college length not significant }
collegelength_exam_HYD <- glm(HYD_NMU ~ factor(COLLEGE_GREEK) + factor(HPC_SELL) + factor(COLLEGE_TYPE) + factor(COLLEGE_SIZE),
                     data = students_US,
                     family = binomial)
tidy(anova(collegelength_exam_HYD, model_initial_HYD, test = "Chisq"))


```


